---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# r2dii.data <img src="man/figures/logo.svg" align="right" width="120" />

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![CRAN status](https://www.r-pkg.org/badges/version/r2dii.data)](https://CRAN.R-project.org/package=r2dii.data)
[![](https://cranlogs.r-pkg.org/badges/grand-total/r2dii.data)](https://CRAN.R-project.org/package=r2dii.data)
[![Codecov test coverage](https://codecov.io/gh/2DegreesInvesting/r2dii.data/branch/main/graph/badge.svg)](https://app.codecov.io/gh/2DegreesInvesting/r2dii.data?branch=main)
[![R-CMD-check](https://github.com/2DegreesInvesting/r2dii.data/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/r2dii.data/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

These datasets support the implementation in R of
the software PACTA (Paris Agreement Capital Transition Assessment),
which is a free tool that calculates the alignment between financial
assets and climate scenarios (<https://2degrees-investing.org/>).
Financial institutions use PACTA to study how their capital
allocation impacts the climate. Because both financial institutions
and market data providers keep their data private, this package
provides fake, public data to enable the development and use of
PACTA in R.

## Installation

Install the released version of r2dii.data from CRAN with:

```r
install.packages("r2dii.data")
```

Or install the development version of r2dii.data with something like this:

```r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/r2dii.data")
```

[How to raise an issue?](https://2degreesinvesting.github.io/posts/2020-06-26-instructions-to-raise-an-issue/)

## Example

```{r example}
library(r2dii.data)

head(data_dictionary)
```

```{r echo=FALSE}
download.file("http://bit.ly/banks-thanks", thanks <- tempfile())
```

## Funding

This project has received funding from the [European Union LIFE
program](https://wayback.archive-it.org/12090/20210412123959/https://ec.europa.eu/easme/en/) and the [International Climate
Initiative
(IKI)](https://www.international-climate-initiative.com/projekt/lenkung-der-finanzstroeme-in-einklang-mit-art-21c-des-paris-abkommens-18-i-351-global-a-paris-and-financial-markets/).
The Federal Ministry for the Environment, Nature Conservation and Nuclear Safety
(BMU) supports this initiative on the basis of a decision adopted by the German
Bundestag. The views expressed are the sole responsibility of the authors and do
not necessarily reflect the views of the funders. The funders are not
responsible for any use that may be made of the information it contains.

